---
title: "Data 607 Assignment 9"
author: "Md. Tanzil Ehsan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
```

## DATA 607 - Assignment 9

The New York Times web site provides a rich set of APIs, as described here: <https://developer.nytimes.com/apis>. We wiil  start by signing up for an API key.

We will  choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.



## Install & Load Required Packages

```{r }
#install.packages("httr")
#install.packages("jsonlite")
#install.packages("tidyverse")  # For data manipulation

```
```{r}
library(httr)
library(jsonlite)
library(tidyverse)

```

## Set my API key in R Using .Renviron 
```{r}
#file.edit("~/.Renviron")


```
## Set API Key
```{r}
api_key <- Sys.getenv("NYTIMES_API_KEY= RXrScA3v9v3wJ2sj4AGy6oAD0dKIaE7V
")

```

```{r}
# to get articles currently on the homepage.
# Define the API URL
url <- paste0("https://api.nytimes.com/svc/topstories/v2/home.json?api-key=RXrScA3v9v3wJ2sj4AGy6oAD0dKIaE7V", api_key)

# Fetch data from API
response <- GET(url)

# Convert response to JSON format
data <- content(response, as = "text", encoding = "UTF-8")
json_data <- fromJSON(data, flatten = TRUE)  # Flatten nested lists

# Convert to Data Frame
nyt_df <- as.data.frame(json_data$results)

# View Data Frame structure
glimpse(nyt_df)

```



## Collecting Data from API 
```{r cars}
url <- paste0('https://api.nytimes.com/svc/topstories/v2/science.json?api-key=RXrScA3v9v3wJ2sj4AGy6oAD0dKIaE7V', Sys.getenv("NYTIMES_API_KEY"))

url2 <- paste0('https://api.nytimes.com/svc/topstories/v2/health.json?api-key=RXrScA3v9v3wJ2sj4AGy6oAD0dKIaE7V', Sys.getenv("NYTIMES_API_KEY"))

science_data <- fromJSON(url)$results %>%
  as.data.frame() %>%
  add_column("web_section" = "Science", .before = "section")

health_data <- fromJSON(url2)$results %>%
  as.data.frame() %>%
  add_column("web_section" = "Health", .before = "section")
```

## View the Data
```{r}
head(science_data )
```
## Data count
```{r}
most_common_subsection <- nyt_df  %>% 
  count(subsection) %>%
  arrange(desc(n)) 
  
most_common_subsection %>%
  knitr::kable(col.names = c("subsection Tag", "Articles counts"))
```

```{r}
# The descriptive tags
most_common_des <- nyt_df  %>% 
  count(des_facet) %>%
  arrange(desc(n))  %>%
filter(n >= 1)
  
most_common_des  %>%
  knitr::kable(col.names = c("subsection Tag", "Counts"))
```

```{r}
# The descriptive tags in science_data
most_common_des <- science_data  %>% 
  count(des_facet) %>%
  arrange(desc(n))  %>%
filter(n >= 1)
  
most_common_des  %>%
  knitr::kable(col.names = c("subsection Tag", "Counts"))
```

## Conclusion:
The goal of this assignment was to get  JSON data from the New York Times API and transform it into an R data frame. We successfully performed the transformation.